Insert the article title here

### 2020-07-22 tex/results.tex
fix fig size
better caption for grid independence

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{cubeL535nm_15Kvs19K.pdf} 
    \caption{Extinction cross section divided by $L^2$ as a function fo wavelength divided by $L$ of
    a cube of size L=535 nm}
    \label{fig:cube535}
 \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{AR_rep_FS4_Ellis2016.pdf} 
    \caption{Replication of figure S4 of supplementary material of Ellis 2016}
    \label{fig:rep_FS4_ellis}
 \end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{cubeL535nm_15Kvs19K.pdf} 
    \caption{Grid independence study for a SiC cube of side L=535 nm, in air under a constant 
    electric field in the z-direction. Extinction cross section divided by $L^2$ as a function of wavelength divided 
    by $L$ of a cube of size L=535 nm}
    \label{fig:cube535}
 \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{AR_rep_FS4_Ellis2016.pdf} 
    \caption{Replication of figure S4 of supplementary material of Ellis 2016}
    \label{fig:rep_FS4_ellis}
 \end{figure}
